Here you can find datasets used throughout the course. I recommend downloading the data in RDS format, since it contains metadata like ordering of ordinal variables. Click on the name to expand.

<details>

<summary class="item">

**Countries**

</summary>

Small datasets on various economic and social indicators of European countries.

You can download the dataset using:

```{r}
#| eval: false

countries <- readr::read_rds("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/countries.rds")
#OR
countries <- read.csv("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/countries.csv")

```

Alternatively, you can download the data from GitHubt in [rds](https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/countries.rds) or [csv](https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/countries.csv) formats.

| Variable        | Label                                                             | Source                |
|:----------------|:------------------------------------------------------------------|:----------------------|
| country         | Country name                                                      |                       |
| code            | Two digit coutry code                                             |                       |
| gdp             | GDP in the milions of EUR (2018)                                  | Eurostat              |
| population      | Country population on the 1.1.2018                                | Eurostat              |
| area            | Area of the country                                               | CIA factbook          |
| eu_member       | Is the country a EU member? (2019)                                | European Union        |
| postsoviet      | Was the country a member of the Eastern block                     | Wikipedia             |
| life_exp        | Life expectancy at birth (2017)                                   | UN                    |
| uni_prc         | \% of people with university education between 15-64 years (2018) | Eurostat              |
| poverty_risk    | \% of people in risk of poverty (2017)                            | Eurostat              |
| material_dep    | \% of people in material deprivation, 3 or less items (2017)      | Eurostat              |
| hdi             | Human development index (2018)                                    | UN                    |
| foundation_date | Date of founding                                                  | Wikipedia             |
| maj_belief      | Biggest religious group (2018)                                    | Pew Researcher Center |

</details>

<details>

<summary class="item">

**United Nations**

</summary>

This is United Nations country level data from 1998, originally used by John Fox in his book [Applied Regression Analysis and Generalized Linear Models](https://socialsciences.mcmaster.ca/jfox/Books/Applied-Regression-3E/index.html).

```{r}
#| eval: false

un <- readr::read_rds("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/united-nations.rds")
#OR
un <- read.csv("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/united-nations.csv")
```

The original data can be downloaded in .txt format [here](https://raw.githubusercontent.com/Sociology-FA-CU/appliedregressioninr/main/data/UnitedNations.txt) (right click and choose *Save link as…*). The description of the data [here](https://socialsciences.mcmaster.ca/jfox/Books/Applied-Regression-3E/datasets/UnitedNations.pdf).

</details>

<details>

<summary class="item">

**Czech Voter Turnout 2017**

</summary>

Aggregated data on the voter turnout by age in the Czech 2017 parliamentary elections from the 8th round of the European Social Survey.

You can download the dataset using:

```{r}
#| eval: false

turnout <- readr::read_rds("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/vote-2017-parliament.rds")
#OR
turnout <- read.csv("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/vote-2017-parliament.csv")
```

Or you can download the data either in [rds](https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/vote-2017-parliament.rds) or [csv](https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/vote-2017-parliament.csv) format.

</details>

<details>

<summary class="item">

**Teachers Beauty and Ratings (**Hamermesh & Parker 2005)

</summary>

The data are gathered from end of semester student evaluations for 463 courses taught by a sample of 94 professors from the University of Texas at Austin. In addition, six students rate the professors' physical appearance. Originally published in [Hamermesh & Parker (2005)](https://fairmodel.econ.yale.edu/ec438/ham1.pdf).

```{r}
#| eval: false

teachers <- readr::read_csv("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/teacher-ratings.csv")

```

</details>

<details>

<summary class="item">

**House Prices in Ames, Iowa (**De Cock, 2011))

</summary>

A data set from [De Cock (2011)](https://jse.amstat.org/v19n3/decock.pdf) has 82 fields were recorded for 2,930 properties in Ames IA. This version is from `tidymodels package`, which in turn copies from the `AmesHousing` package but does not include a few quality columns that appear to be outcomes rather than predictors. Variable description can be found [here](https://jse.amstat.org/v19n3/decock/DataDocumentation.txt).

```{r}
#| eval: false

ames <- readr::read_rds("https://github.com/Sociology-FA-CU/applied-regression-r/raw/main/data/ames.rds")
#OR
ames <- readr::read_csv("https://raw.githubusercontent.com/Sociology-FA-CU/applied-regression-r/main/data/ames.csv")

```

</details>
